Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-12 papers/LREC2020/survey.tex
lrec camera ready, correcting 2 small issues identified by Carina

However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
For instance, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, the annotation suggests that \textit{bird} is the only available name. 
The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (5\%) seem to be an effect of this partial linking problem.
We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.\ truly overlapping objects).

>>>>

However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
For instance, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, the annotation suggests that \textit{bird} is the only available name. 
The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (2\%) seem to be an effect of this partial linking problem.
We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.\ truly overlapping objects).
